Improving credibility and efficiency of decision-making \\ within democratic communities via statistical quorum

### 2018-04-19 statistical-quorum.tex
Things were less clear.

In Figure~\ref{fig:survey-comparison} we see questions and results of the survey we made at the end of each semester.

We can see that in fall members were more satisfied with the decision making in the community and only how understandable
is the whole process received a decrease. We attribute this to the fact that the use of the web application is
a novelty and requires more effort in educating members than a traditional decision making. Moreover, decision
making in person allows one to observe others how they are participating and learn from them, instead of
being alone using the application.

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{figures/survey-comparison.pdf}
\caption{Results of a survey at the end of spring and fall semesters about general perception of the decision making (councils) in the community.
For each question, a participant was asked to rank the answer on a scale between 1 (completely disagree) and 7 (completely agree). All members
of the community were invited to participate in the survey each time.}
\label{fig:survey-comparison}
\end{figure}

\subsection{Interviews}

>>>>

In Figure~\ref{fig:survey-comparison} we see questions and results of the survey we made at the end of both semesters.

We can see that in fall members were more satisfied with the decision making in the community and only how understandable
is the whole process decreased.
We attribute this to the fact that the use of the web application is
a novelty, including using a novel concept like statistical quroum, and requires more effort
in educating members than a traditional decision making.
Moreover, decision making in person allows one to observe others how they are participating and
learn from them, instead of being alone using the application.
We explore this question also through interviews in Section~\ref{sec:interviews}.

\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{figures/survey-comparison.pdf}
\caption{Results of a survey at the end of spring (baseline) and fall (using PeerMind) semesters about general perception of the decision making (councils) in the community.
For each question, a participant was asked to rank the answer on a scale between 1 (completely disagree) and 7 (completely agree). All members
of the community were invited to participate in the survey each time.}
\label{fig:survey-comparison}
\end{figure}

\subsection{Interviews}
\label{sec:interviews}
